Historical Supply of Residual Biomass from Timber Harvest in West-central Alberta, Canada

### 2021-10-08 analysis/get_util_piece_size.Rmd
new residue values

```{r libraries, echo=FALSE, message=FALSE}
setwd("/mnt/chromeos/GoogleDrive/SharedDrives/FES_Data_Sharing_Forestry/Manuscripts/histressupp/analysis")
#setwd("g:/Shared Drives/FES_Data_Sharing_Forestry/Manuscripts/histressupp/analysis")

>>>>

```{r libraries, echo=FALSE, message=FALSE}
#setwd("/mnt/chromeos/GoogleDrive/SharedDrives/FES_Data_Sharing_Forestry/Manuscripts/histressupp/analysis")
setwd("g:/Shared Drives/FES_Data_Sharing_Forestry/Manuscripts/histressupp/analysis")

### 2021-10-08 analysis/manuscript.Rmd
new residue values

---
title: "Historical Supply of Residual Biomass from Timber Harvest in West-central Alberta, Canada"
author:
- Glen W. Armstrong^[Department of Renewable Resources, University of Alberta]
- Jay A. Anderson^[Department of Resource Economics and Environmental Sociology, University
  of Alberta]
- Alex W. McPhee^[Department of Resource Economics and Environmental Sociology, University
  of Alberta]
date: "`r format(Sys.time(), '%Y-%m-%d')`"
#date: "2021-10-05"
output:
  html_document:
    df_print: paged
  word_document:
  pdf_document:
    number_sections: yes
    latex_engine: xelatex
    keep_tex: yes
csl: canadian-journal-of-forest-research
#csl: biomass-and-bioenergy
bibliography: historicalResidueSupply.bib
---

@@

```{r libraries, echo=FALSE, message=FALSE}
#setwd("/home/gwa/Work/historical-residue/Analysis")
#setwd("g:/Shared drives/FES_Data_Sharing (Forestry)/Manuscripts/Historical ResidueSupply/Analysis")
setwd("/mnt/chromeos/GoogleDrive/SharedDrives/FES_Data_Sharing_Forestry/Manuscripts/histressupp/analysis")
library(tidyverse)
library(ggthemes)
library(gridExtra)
library(viridis)
library(skimr)
library(scales)
library(DescTools)
library(zoo)
library(ezknitr)
#ezknit(file="analysis/manuscript.Rmd", out_dir="output", fig_dir="myfigs")
```

@@

@@

```{r read_data_files, echo=FALSE}
t <- read.csv(file = '../data/township_merchantable_volume.csv')
twp_merch_vol <- t %>% select(c(TRM,mean_merch_volume)) 
twp_merch_vol$adj_vol <- twp_merch_vol$mean_merch_volume * merch_vol_adj_factor
twp_merch_vol$residue_odmt <- twp_merch_vol$adj_vol * odmt_adj_factor

t <- read.csv(file = '../data/harvest_township_stats_melt_area.csv')
t <- subset(t, select = c(TRM,year,harvest_ha)) %>% filter(year >=1990)
t <- merge(t, twp_merch_vol, by = "TRM", all=TRUE)
t$adj_vol <- t$adj_vol %>% replace_na(0)  # there is an NAs problem here.  replace NAs with average.
                                              # is that the right way to do it?
t$harvest_vol <- t$harvest_ha * t$adj_vol 
t$residue_odmt <- t$harvest_vol * odmt_adj_factor

@@

Dennis Gray contributed to data collection.  Funding was provided by Future Energy Systems, University of Alberta.

>>>>

---
title: "Historical Supply of Residual Biomass from Timber Harvest in West-central Alberta, Canada"
author:
- Glen W. Armstrong^[Department of Renewable Resources, University of Alberta]
- Jay A. Anderson^[Department of Resource Economics and Environmental Sociology, University
  of Alberta]
- Alex W. McPhee^[Department of Resource Economics and Environmental Sociology, University
  of Alberta]
date: "`r format(Sys.time(), '%Y-%m-%d')`"
#date: "2021-10-05"
output:
  pdf_document:
    number_sections: yes
    latex_engine: xelatex
    keep_tex: yes
  word_document:
  html_document:
    df_print: paged
csl: canadian-journal-of-forest-research
#csl: biomass-and-bioenergy
bibliography: historicalResidueSupply.bib
---

@@

```{r libraries, echo=FALSE, message=FALSE}
#setwd("/home/gwa/Work/historical-residue/Analysis")
setwd("g:/Shared drives/FES_Data_Sharing_Forestry/Manuscripts/histressupp")
#setwd("/mnt/chromeos/GoogleDrive/SharedDrives/FES_Data_Sharing_Forestry/Manuscripts/histressupp/analysis")
library(tidyverse)
library(ggthemes)
library(gridExtra)
library(viridis)
library(skimr)
library(scales)
library(DescTools)
library(zoo)
library(ezknitr)
#ezknit(file="analysis/manuscript.Rmd", out_dir="output", fig_dir="myfigs")
```

@@

@Peltola2011

@@

```{r read_data_files, echo=FALSE}
t <- read.csv(file = '../data/township_merchantable_volume.csv')
twp_merch_vol <- t %>% select(c(TRM,mean_merch_volume)) 
twp_merch_vol$adj_vol <- twp_merch_vol$mean_merch_volume * merch_vol_adj_factor
#twp_merch_vol$residue_odmt <- twp_merch_vol$adj_vol * odmt_adj_factor
load("../data/biomass_by_trm.RData")
twp_merch_vol <- merge(twp_merch_vol,biomass_by_trm,by = "TRM", all = TRUE)
twp_merch_vol <- twp_merch_vol %>% 
  mutate(adj_factor = res_total/adj_vol)

mean(twp_merch_vol$adj_factor)

t <- read.csv(file = '../data/harvest_township_stats_melt_area.csv')
t <- subset(t, select = c(TRM,year,harvest_ha)) %>% filter(year >=1990)
t <- merge(t, twp_merch_vol, by = "TRM", all=TRUE)
t$adj_vol <- t$adj_vol %>% replace_na(0)  # there is an NAs problem here.  replace NAs with average.
                                              # is that the right way to do it?
t$harvest_vol <- t$harvest_ha * t$adj_vol 
t$residue_odmt <- t$harvest_ha * t$res_total
t <- t %>% 
  filter(!is.na(residue_odmt))

@@

This research was supported by funding from the Canada First Research Excellence Fund as part of the University of Alberta’s Future Energy Systems research initiative.

Dennis Gray contributed to data compilation.
